Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2014-10-09 Report/mse_formulation.tex
modified with markku input

In this section, we solve the \ac{JSFRA} problem by exploiting the equivalence between the \ac{MSE} and the achievable capacity for the receivers designed based on the \ac{MMSE} criterion \cite{viswanath1999optimal,mse_duality}. The \ac{MSE} \me{\epsilon_{l,k,n}}, for the data symbol is given by
\iftoggle{single_column}{
\begin{multline} \label{mse-error}
	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \\
	+ \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 = \epsilon_{l,k,n},
\end{multline}
}{
\begin{multline} \label{mse-error}
 \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \\
 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 = \epsilon_{l,k,n},
\end{multline}
}
where \me{\mvec{m}{l,k,n}, \mvec{w}{l,k,n}} denotes the transmit and the receive beamformer and \me{\hat{d}_{l,k,n}} is the received symbol as in \eqref{eqn-1}. Now, replacing the receive beamformer in \eqref{mse-error} with the \ac{MMSE} receiver shown in \eqref{eqn-10}, we obtain the following relation between the \ac{MSE} and the \ac{SINR} as
\begin{equation} \label{eqn-mse-eq}
\epsilon_{l,k,n} = \frac{1}{1 + \gamma_{l,k,n}},
\end{equation}
where \me{\gamma_{l,k,n}} is the received \ac{SINR} as in \eqref{eq:SINR}. Using the equivalence in \eqref{eqn-mse-eq}, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} equivalent to obtain the precoders for the \acs{MU}-\acs{MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi,hong2012decomposition}.

Let \me{{v}^{\prime}_k = Q_k - \sum_{n=1}^N \sum_{l=1}^L t_{l,k,n}} denote the queue deviation corresponding to the user \me{k} and \me{\tilde{{v}}^{\prime}_k \triangleq a_k^{1/{q}}v^{\prime}_k} represents the weighted equivalent. Now, by relaxing the \ac{MSE} in \eqref{mse-error} and the rate  \ac{MSE} equivalence, \eqref{eqn-6} is written as
\iftoggle{single_column}{
\begin{IEEEeqnarray}{rCl}\label{eqn-mse-1}
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \quad & \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
\text{subject to} & \quad & t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}) \IEEEyessubnumber \label{eqn-mse-1.2} \\
 & \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \eqspace \IEEEyessubnumber \label{eqn-mse-1.3} \\
& \quad &  \text{and} \; \eqref{eqn-4.3}.  \IEEEyessubnumber \label{eqn-mse-1.4}
\end{IEEEeqnarray}
}{{\allowdisplaybreaks
\begin{IEEEeqnarray}{CL}\label{eqn-mse-1}
	\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \quad \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
	\text{subject to} & \quad t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}) \IEEEyessubnumber \label{eqn-mse-1.2} \\
	& \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \nonumber \\
	& {} + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 \leq \epsilon_{l,k,n}\IEEEyessubnumber \label{eqn-mse-1.3} \\
	&  \text{and} \; \eqref{eqn-4.3}. \IEEEyessubnumber \label{eqn-mse-1.4}
\end{IEEEeqnarray}}}

The alternative \ac{MSE} formulation given by \eqref{eqn-mse-1} is non-convex even for the fixed \me{\mvec{w}{l,k,n}} due to the constraint \eqref{eqn-mse-1.2}. We adopt the \ac{SCA} method as in Section \ref{sec-3.2} to relax the constraint by a sequence of convex subsets using first order approximations around \me{\tilde{\epsilon}_{l,k,n}} as
\begin{IEEEeqnarray}{rCl}
- \log_2(\tilde{\epsilon}_{l,k,n}) - \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2) \, \tilde{\epsilon}_{l,k,n}} &\geq& t_{l,k,n},
\label{mse-lin}
\end{IEEEeqnarray}

Now, using the above approximation for the rate constraint, the problem defined by \eqref{eqn-mse-1} can be solved optimal transmit precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}} and the users rates over each sub-channel \me{t_{l,n,k}} for the fixed receive beamformers. Once the optimal precoders are obtained, the local \ac{MSE} variable  \me{\tilde{\epsilon}_{l,k,n}} is updated with the current update \me{\epsilon_{l,k,n}}. The optimization problem for a fixed receive beamformers \me{\mvec{w}{l,k,n}} is given as
\begin{IEEEeqnarray}{CCl}\label{eqn-mse-2}
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\epsilon_{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
\text{subject to} & \quad & \eqref{eqn-4.3},\, \eqref{eqn-mse-1.3},\,\text{and} \:\eqref{mse-lin}. \IEEEyessubnumber \label{eqn-mse-2.2}
\end{IEEEeqnarray}
\subsubsection*{Convergence}
Following the similar approach in Section \ref{sec-3.2.1}, at each iteration, the \ac{SCA} subproblems converge to a stationary point of the original nonconvex problem. The uniqueness of the precoders are justified if there is no phase ambiguity in the stationary solution. By reorganizing \eqref{eqn-mse-1.3}
\iftoggle{single_column}{
\begin{equation}
\epsilon_{l,k,n} \geq  1 - 2 \Re{ \left \lbrace \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right \rbrace} + \sum_{\mathclap{\forall (j,i)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2,
\end{equation}
}{
\begin{multline}
	\epsilon_{l,k,n} \geq  1 - 2 \Re{ \left \lbrace \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right \rbrace} \\ 
	+ \sum_{\mathclap{\forall (j,i)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2,
\end{multline}
}
we can see that the ambiguity in the phase rotations for the transmit and the receive beamformers are avoided by the real component in the \ac{MSE} expression.

At each \ac{SCA} step, the transmit precoders are obtained uniquely by minimizing \eqref{eqn-mse-1} due to the convex nature of the relaxed problem. Using the transmit precoders, the receive beamformers are obtained using the \ac{MMSE} receivers. The \ac{MMSE} receiver minimizes the objective value for the fixed transmit precoders, leading to the monotonic convergence of the objective function. At each \ac{SCA} step, the optimal value of the previous iteration is also included in the domain of the problem, the objective value can either decrease or stays the same after each iteration.

>>>>

In this section, we solve the \ac{JSFRA} problem by exploiting the equivalence between the \ac{MSE} and the achievable sum rate for the receivers designed based on the \ac{MMSE} criterion \cite{viswanath1999optimal,mse_duality}. The \ac{MSE} \me{\epsilon_{l,k,n}}, for the data symbol is given by
\iftoggle{single_column}{
\begin{multline} \label{mse-error}
	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \\
	+ \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 = \epsilon_{l,k,n},
\end{multline}
}{
\begin{multline} \label{mse-error}
 \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \\
 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 = \epsilon_{l,k,n},
\end{multline}
}
where \me{\hat{d}_{l,k,n}} is the estimate of the transmitted symbol. Now, replacing the receive beamformer in \eqref{mse-error} with the \ac{MMSE} receiver in \eqref{eqn-10}, we obtain the following relation between the \ac{MSE} and the \ac{SINR} as
\begin{equation} \label{eqn-mse-eq}
\epsilon_{l,k,n} = \frac{1}{1 + \gamma_{l,k,n}},
\end{equation}
where \me{\gamma_{l,k,n}} is the received \ac{SINR} as in \eqref{eq:SINR}. Using the equivalence in \eqref{eqn-mse-eq}, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} equivalent to obtain the precoders for the \acs{MU}-\acs{MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi,hong2012decomposition}.

Let \me{{v}^{\prime}_k = Q_k - \sum_{n=1}^N \sum_{l=1}^L t_{l,k,n}} denote the queue deviation corresponding to user \me{k} and \me{\tilde{{v}}^{\prime}_k \triangleq a_k^{1/{q}}v^{\prime}_k} represents the weighted equivalent. By using the relaxed \ac{MSE} expression in \eqref{mse-error}, the problem in \eqref{eqn-3} can be expressed as
\iftoggle{single_column}{
\begin{IEEEeqnarray}{rCl}\label{eqn-mse-1}
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \quad & \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
\text{subject to} & \quad & t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}) \IEEEyessubnumber \label{eqn-mse-1.2} \\
 & \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \eqspace \IEEEyessubnumber \label{eqn-mse-1.3} \\
& \quad &  \text{and} \; \eqref{eqn-4.3}.  \IEEEyessubnumber \label{eqn-mse-1.4}
\end{IEEEeqnarray}
}{{\allowdisplaybreaks
\begin{IEEEeqnarray}{CL}\label{eqn-mse-1}
	\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \quad \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
	\text{subject to} & \quad t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}) \IEEEyessubnumber \label{eqn-mse-1.2} \\
	& \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \nonumber \\
	& {} + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 \leq \epsilon_{l,k,n}\IEEEyessubnumber \label{eqn-mse-1.3} \\
	&  \text{and} \; \eqref{eqn-4.3}. \IEEEyessubnumber \label{eqn-mse-1.4}
\end{IEEEeqnarray}}}

An alternative \ac{MSE} formulation given by \eqref{eqn-mse-1} is non-convex even for the fixed \me{\mvec{w}{l,k,n}} due to the constraint \eqref{eqn-mse-1.2}. We adopt the \ac{SCA} method as in Section \ref{sec-3.2} to relax the constraint by a sequence of convex subsets using first order Taylor series approximation around a fixed \ac{MSE} point  \me{\tilde{\epsilon}_{l,k,n}} as
\begin{IEEEeqnarray}{rCl}
- \log_2(\tilde{\epsilon}_{l,k,n}) - \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2) \, \tilde{\epsilon}_{l,k,n}} &\geq& t_{l,k,n},
\label{mse-lin}
\end{IEEEeqnarray}

Using the above approximation for the rate constraint, the problem defined in \eqref{eqn-mse-1} is solved for optimal transmit precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}}, and the user rates over each sub-channel \me{t_{l,n,k}} given the fixed receive beamformers. Once the optimal precoders are obtained, the local \ac{MSE} variable  \me{\tilde{\epsilon}_{l,k,n}} is updated with the current update \me{\epsilon_{l,k,n}}. The optimization problem for a fixed receive beamformers \me{\mvec{w}{l,k,n}} is given as
\begin{IEEEeqnarray}{CCl}\label{eqn-mse-2}
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\epsilon_{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
\text{subject to} & \quad & \eqref{eqn-4.3},\, \eqref{eqn-mse-1.3},\,\text{and} \:\eqref{mse-lin}. \IEEEyessubnumber \label{eqn-mse-2.2}
\end{IEEEeqnarray}
\subsubsection*{Convergence}
Following similar approach as in Section \ref{sec-3.2.1}, at each iteration, the \ac{SCA} subproblems converge to a stationary point of the original nonconvex problem. The uniqueness of the precoders are justified if there is no phase ambiguity in the stationary solution. By reorganizing \eqref{eqn-mse-1.3}
\iftoggle{single_column}{
\begin{equation}
\epsilon_{l,k,n} \geq  1 - 2 \Re{ \left \lbrace \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right \rbrace} + \sum_{\mathclap{\forall (j,i)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2,
\end{equation}
}{
\begin{multline}
	\epsilon_{l,k,n} \geq  1 - 2 \Re{ \left \lbrace \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right \rbrace} \\ 
	+ \sum_{\mathclap{\forall (j,i)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2,
\end{multline}
}
we can see that the ambiguity in the phase rotations for the transmit and the receive beamformers are eliminated by the presence of real component in the \ac{MSE} expression.

At each \ac{SCA} iteration, the transmit precoders are obtained uniquely by minimizing \eqref{eqn-mse-1} due to the convex nature of the relaxed problem. Using the transmit precoders, the receive beamformers are obtained using the \ac{MMSE} receivers. The \ac{MMSE} receiver minimizes the objective value for the fixed transmit precoders, leading to the monotonic convergence of the objective function. At each \ac{SCA} step, the optimal value of the previous iteration is also included in the domain of the problem, and the objective value can either decrease or stays the same after each iteration.

### 2014-10-09 Report/primal_approach.tex
modified with markku input

The \acl{PD} approach decomposes the problem by fixing the interference variables \me{\zeta_{l,k,n,b} \forall k,b} in order to perform the precoder design independently across each \ac{BS}. Once the optimal precoders are designed at each \ac{BS} with the fixed interference constraints \eqref{eqn-decent-3}, the dual variables corresponding to the interference constraints are exchanged between the cooperating \acp{BS} in \me{\mc{B}} to update the interference variables \me{\zeta_{l,k,n,b}} for the next iteration until convergence. The primal approach is discussed extensively for the min-power problem in \cite{pennanen2011decentralized} and much of the current work follows the same. 
%Much of the details are provided in the Appendix \ref{a-2}.

\subsubsection*{Convergence}
The convergence of the primal is similar to that of the centralized problem if the interference variables \me{\zeta_{l,k,n,b}} are allowed to converge to a stationary point. But in practice, we can limit the number of exchanges to \me{J_{\max}} after which \ac{SCA} update is performed until convergence or for \me{I_{\max}} times. The update of \me{\tilde{p}_{l,k,n}, \tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}} can be made in conjunction with the receiver update \me{\mvec{W}{k,n}}. The receiver update can be made by using the precoded pilot transmission from each user as in \cite{komulainen2013effective}.

>>>>

The \acl{PD} approach decomposes the problem by fixing the interference variables \me{\zeta_{l,k,n,b} \forall k,b} in order to perform the precoder design independently across each \ac{BS}. Once the optimal precoders are designed at each \ac{BS} with the fixed interference constraints \eqref{eqn-decent-3}, the dual variables corresponding to the interference constraints are exchanged between the cooperating \acp{BS} in \me{\mc{B}} to update the interference variables \me{\zeta_{l,k,n,b}} for the next iteration until convergence. The primal approach is discussed extensively for the min-power problem in \cite{pennanen2011decentralized} and much of the current work follows similar approach. 
%Much of the details are provided in the Appendix \ref{a-2}.

\subsubsection*{Convergence}
The convergence of the primal decomposition is similar to that of the centralized problem if the interference variables \me{\zeta_{l,k,n,b}} are allowed to converge to a stationary point. In practice, we can limit the number of exchanges to \me{J_{\max}} after which the \ac{SCA} update is performed until convergence or for \me{I_{\max}} times. The update of \me{\tilde{p}_{l,k,n}, \tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}} can be made in conjunction with the receiver update \me{\mvec{W}{k,n}}. The receiver update can be made by using the precoded pilot transmission from each user as in \cite{komulainen2013effective}.

### 2014-10-09 Report/problem_formulation.tex
markku_modifications
halfcooked
modified with markku input

The problem defined in \eqref{q_gen_sum} ignores the second order term arising from the Lyapunov drift minimization objective by the limiting it to a constant value. In fact, Eq. \eqref{eqn-4.2} provides similar expression when the exponent is set to be \me{\ell_{q=2}} as
\begin{equation}\label{pf-1}
\underset{t_k}{\text{minimize}} \, \sum_k \, v_k^2 = \underset{t_k}{\text{minimize}} \, \sum_k \, Q_k^2 - 2 \, Q_k t_k + t_k^2
\end{equation}
It is evident that \eqref{pf-1} is equivalent to \eqref{backpressure-approx} if the second order terms are ignored. Limiting \me{t_k^2} by a constant value, the \ac{Q-WSRM} formulation requires the explicit rate constraint \eqref{eqn-3.1.4} to avoid the resource wastage in the form of over allocation. In the proposed queue deviation formulation, the explicit rate constraint is not needed, since it is handled by the objective function itself. This makes the problem simpler and allows us to employ efficient algorithms to distribute the precoder design problem across each \acp{BS} independently by exchanging minimal information exchange \cite{boyd2011distributed}. In contrast to the \ac{WSRM} formulation, the \ac{JSFRA} and the \ac{Q-WSRM} problems include the sub-channels jointly to achieve an efficient allocation by identifying the optimal space-frequency resource for each user in the system. The queue deviation objective provides an alternative approach to perform the resource allocation without the additional rate constraints as in \ac{Q-WSRME} approach.

>>>>

The problem defined in \eqref{q_gen_sum} ignores the second order term arising from the Lyapunov drift minimization objective by limiting it to a constant value. In fact, \eqref{eqn-4.2} provides similar expression when the exponent is set to be \me{\ell_{q=2}} as
\begin{equation}\label{pf-1}
\underset{t_k}{\text{minimize}} \, \sum_k \, v_k^2 = \underset{t_k}{\text{minimize}} \, \sum_k \, Q_k^2 - 2 \, Q_k t_k + t_k^2.
\end{equation}

It is evident that \eqref{pf-1} is equivalent to \eqref{backpressure-approx} if the second order terms are ignored. Limiting \me{t_k^2} by a constant value, the \ac{Q-WSRM} formulation requires the explicit rate constraint \eqref{eqn-3.1.4} to avoid the resource wastage in the form of over-allocation. In the proposed queue deviation formulation, the explicit rate constraint is not needed, since it is handled by the objective function itself. This makes the problem simpler and allows us to employ efficient algorithms to distribute the precoder design problem across each \acp{BS} independently by exchanging minimal information exchange \cite{boyd2011distributed}. In contrast to the \ac{WSRM} formulation, the \ac{JSFRA} and the \ac{Q-WSRM} problems include the sub-channels jointly to achieve an efficient allocation by identifying the optimal space-frequency resource for each user in the system. The queue deviation objective provides an alternative approach to perform the resource allocation without the additional rate constraints as in the \ac{Q-WSRME} formulation.
